Notes of Topological Transition in a Non-Hermitian Quantum Walk

### 2016-12-08 Notes of various papers/Topological Transition in a Non-Hermitian Quantum Walk/notes.tex
[minor]Add a sample output for the numerical test of $p_k$ and $u_k$

I was doubtful of the fact that $p_k$ is even in $k$, so I did a
numerical check (see file
"{OneD\_quantum\_walk\_test\_even\_functions\_pk\_uk.m}"), and
unfortunately my guess seems to be wrong. I have given arbitrary
numbers to time $t$, $v$, $v'$, energies $\varepsilon_R$ and
$\varepsilon_L$, and the resulted $p_k$ is always even in $k$, the
resulted $u_k$ is always constantly $0$ in both time variable $t$ and $k$.

>>>>

I was doubtful of the fact that $p_k$ is even in $k$, so I did a
numerical check (see file
"{OneD\_quantum\_walk\_test\_even\_functions\_pk\_uk.m}"), and
unfortunately my guess seems to be wrong. I have given arbitrary
numbers to time $t$, $v$, $v'$, energies $\varepsilon_R$ and
$\varepsilon_L$, and the resulted $p_k$ is always even in $k$, the
resulted $u_k$ is always constantly $0$ in both variables $t$ and $k$.
So $\partial_t u_k$ is trivially even in $k$. Below are to typical
outputs:

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/Sample-output-for-p_k.eps}
    \caption{Sample output for $p_k$}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{pics/Sample-output-for-u_k.eps}
    \caption{Sample output for $u_k$}
\end{figure}
